Analysis and figures

### 2024-10-14 Supplement/Analysis.qmd
Changes during article submission

---
title: "Analysis and figures"
author: "Saoirse Kelleher"
date: today
abstract: "Calculates key statistics and renders figures for \"*Twenty years of dynamic occupancy models: a review of applications and look to the future*\""
abstract-title: "Summary"
format:
  html:
    theme: minty
---

@@

```{r Load query sheets}
sheet_AllArticles <- list(read_xlsx("Randomisation/Randomisation.xlsx", 
                                    sheet = "2004-2007"),
                          read_xlsx("Randomisation/Randomisation.xlsx", 
                                    sheet = "2008-2011"),
                          read_xlsx("Randomisation/Randomisation.xlsx", 
                                    sheet = "2012-2015"),
                          read_xlsx("Randomisation/Randomisation.xlsx", 
                                    sheet = "2016-2019"),
                          read_xlsx("Randomisation/Randomisation.xlsx", 
                                    sheet = "2020-2023")) |> 
  list_rbind()
```

@@

The next set of statistics and figures focus on the study areas included in reviewed articles. For each article the countries where data was collected, a rough centroid of the study area, and an estimate of the spatial extent of the study area was recorded.

@@

First, a table is generated presenting the number of articles using data from each country with at least one article.

@@

::: callout-important
## Articles may include multiple study areas in cases where distinct dataset were modelled separately
:::

```{r Study location map}
# Load country shapefile
countries_shp <- st_read("Analysis/Countries_Spatial/World_Countries__Generalized_.shp", quiet = TRUE) |>
  st_transform(crs = "ESRI:54030") |>
  filter(COUNTRY != "Antarctica")

@@

#### Modelling table

@@

The objectives of each article were documented, split into 6 non-exclusive categories.

@@

@@

We render a second figure for the average number of covariates used in articles approaching each objective

@@

Combine the objective plots

>>>>

---
title: "Analysis and figures"
date: September 26 2024
abstract: "Calculates key statistics and renders figures for \"*Twenty years of dynamic occupancy models: a review of applications and look to the future*\""
abstract-title: "Summary"
format:
  html:
    theme: minty
embed-resources: true
---

@@

```{r Load query sheets}
sheet_AllArticles <- list(read_xlsx("Randomisation.xlsx", 
                                    sheet = "2004-2007"),
                          read_xlsx("Randomisation.xlsx", 
                                    sheet = "2008-2011"),
                          read_xlsx("Randomisation.xlsx", 
                                    sheet = "2012-2015"),
                          read_xlsx("Randomisation.xlsx", 
                                    sheet = "2016-2019"),
                          read_xlsx("Randomisation.xlsx", 
                                    sheet = "2020-2023")) |> 
  list_rbind()
```

@@

The next set of statistics and figures focus on the study areas included in reviewed articles. For each article the countries where data was collected, a rough centroid of the study area and an estimate of the spatial extent of the study area was recorded.

@@

First, a table is generated presenting the number of articles using data from each country.

@@

::: callout-important
## Articles may include multiple study areas in cases where distinct datasets were modelled separately
:::

```{r Study location map}
# Load country shapefile
countries_shp <- st_read("Spatial/World_Countries__Generalized_.shp", quiet = TRUE) |>
  st_transform(crs = "ESRI:54030") |>
  filter(COUNTRY != "Antarctica")

@@

In this section, we gather information on practices in the modelling process to generate a summary table. This involves aspects including the median number of covariates per parameter, the proportion of studies using different model selection approaches, and the proportion of studies evaluating their models. This data is split between Bayesian and Frequentist models.

@@

In this section we summarise information on the objectives of each study. Objectives were described in six non-exclusive categories.

@@

We generate a plot (Figure 6 in the review) showing two elements related to objectives. First, we calculate the proportion of articles in each year-strata pursuing each objective.

@@

We then render a second figure for the average number of covariates used in articles approaching each objective.

@@

We combine the objective plots using the `patchwork` package.
